---
title: "Perceptual stability ilution"
output: html_document
date: "2023-06-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
## Import data

```{r}
root <- rprojroot::is_rstudio_project
basename(getwd())

# load dataframe 
filepath <- root$find_file("pilot_2/df_exp_filter_long.Rda")
load(file= filepath)

df_exp <- df_exp_filter_long
rm(df_exp_filter_long)
```

## Explore df
```{r}
str(df_exp)
head(df_exp)
```

## Exploratory analysis on AQ

```{r}
library(dplyr)
library(ggplot2)

# grouped df
df_exp_grouped <- df_exp %>% 
  group_by(participants) %>%
  summarise(across(everything(), first))

```


AQ total score
```{r}
# total score
hist(df_exp_grouped$AQ)
summary(df_exp_grouped$AQ)
```

AQ total score by sex
```{r}

# For male
paste("For male: ")
summary(df_exp_grouped[df_exp_grouped$sex == "Male",]$AQ)

# For female
paste("For female: ")
summary(df_exp_grouped[df_exp_grouped$sex == "Female",]$AQ)
```

Not very similar with previous literature (female:15.4; male: 17.8; Baron-Cohen et al., 2001).
Not usual female scoring more than male on AQ.

## Exploratory analysis on face/dots stimuli

```{r}
df_exp %>%
  group_by(stimulus) %>%
  summarise(mean = mean(response), 
            median = median(response),
            se = sd(response)/sqrt(length(response)),
            sd = sd(response))

```
It's kind of weird, because the mean shows that in the dot stimuli there is no apparent effect, but the median does show that there would be an apparent effect. Check the distribution, they may not be Gaussian.

I discard those responses that are 3 deviations away from the mean of their respective group.
```{r}
# Calculates the mean and standard deviation for each stimulus.
stimulus_stats <- df_exp %>%
  group_by(stimulus) %>%
  summarize(
    mean_response = mean(response),
    sd_response = sd(response)
  )

# Join the statistics back to the original dataframe.
df_exp_with_stats <- df_exp %>%
  left_join(stimulus_stats, by = "stimulus")

# Filter out responses that are more than 3 standard deviations away from the mean.
df_exp_filtered <- df_exp_with_stats %>%
  filter(abs(response - mean_response) <= 2 * sd_response)
```


I test the other distributions
```{r}
p <- df_exp_filtered %>% 
  ggplot(aes(response)) + 
  geom_histogram(binwidth = 5, fill = "blue", color = "black") +
  ggtitle("Response Histogram") + 
  xlab("Response") + 
  ylab("Count") +
  facet_wrap(~ stimulus) 

# Calcula media y mediana por grupo  
summarized <- df_exp %>% 
  group_by(stimulus) %>% 
  summarize(
    mean = mean(response), 
    median = median(response)
  )

# Agrega las líneas verticales al gráfico base
p + 
  geom_vline(data = summarized, aes(xintercept = mean), color = "black", linetype = "solid") +
  geom_vline(data = summarized, aes(xintercept = median), color = "black", linetype = "dashed") 

```

```{r}
df_exp_filtered %>%
  group_by(stimulus) %>%
  summarise(mean = mean(response), 
            median = median(response),
            se = sd(response)/sqrt(length(response)),
            sd = sd(response))

```


It is interesting to see that the two versions of the face stimulus do show differences between them, I don't know if they are significant, but you can see differences in mean and median. Check if significant differences are observed.

fs1yo vs fs2yo
```{r}
fs1yo <- df_exp %>%
  filter(stimulus == "videos/fs1yo.mp4")

fs2yo <- df_exp %>%
  filter(stimulus == "videos/fs2yo.mp4")

# U the Mann Whitney
wilcox.test(fs1yo$response,fs2yo$response)
```

fs1o vs fs2o
```{r}
fs1o <- df_exp %>%
  filter(stimulus == "videos/fs1o.mp4")

fs2o <- df_exp %>%
  filter(stimulus == "videos/fs2o.mp4")

# U the Mann Whitney
wilcox.test(fs1o$response,fs2o$response)
```

fs1y vs fs2y
```{r}
fs1y <- df_exp %>%
  filter(stimulus == "videos/fs1y.mp4")

fs2y <- df_exp %>%
  filter(stimulus == "videos/fs2y.mp4")

# U the Mann Whitney
wilcox.test(fs1y$response,fs2y$response)
```

There seemed to be differences, but these are not significant. Perhaps because of the size of the sd they present, compared to the difference in means.



Now, I'm going to get two attraction indexes per participant. One will be based on the face stimulus (fs1yo or fs2yo) of the test that was used with the participant, and the second one will be based on the dot stimulus.

DEFINITION 1
"Attraction index was computed by calculating the ratio between the test rating (e.g., old test face) and the absolute difference between the two reference face ratings (e.g., young and old)." Manassi & Whitney, 2022.

In general for dots
```{r}
test_stm_dot <- df_exp %>%
  filter(stimulus == "dot_40_60") %>%
  select(response) 

reference_few_dot <- df_exp %>%
  filter(stimulus == "dot_40") %>%
  select(response) 

reference_many_dot <- df_exp %>%
  filter(stimulus == "dot_60") %>%
  select(response) 

## with the mean
print("with the mean: ")
mean(test_stm_dot$response)/abs(mean(reference_few_dot$response) - mean(reference_many_dot$response))
## with the median
print("with the median: ")
median(test_stm_dot$response)/abs(median(reference_few_dot$response) - median(reference_many_dot$response))

```
In general for faces
```{r}
test_stm_face <- df_exp %>%
  filter(stimulus == "videos/fs1yo.mp4" | stimulus == "videos/fs2yo.mp4") %>%
  select(response) 

reference_few_face <- df_exp %>%
  filter(stimulus == "videos/fs1y.mp4" | stimulus == "videos/fs2y.mp4") %>%
  select(response) 

reference_many_face <- df_exp %>%
  filter(stimulus == "videos/fs1o.mp4" | stimulus == "videos/fs2o.mp4") %>%
  select(response) 

## with the mean
print("with the mean: ")
mean(test_stm_face$response)/abs(mean(reference_few_face$response) - mean(reference_many_face$response))
## with the median
print("with the median: ")
median(test_stm_face$response)/abs(median(reference_few_face$response) - median(reference_many_face$response))

```

Per participant for dots. 

Here I can also observe two ways, and a decision to make. When I calculated de attraction index individually, I could use the individuals responses for the test stimuli and also the individuals responses for the reference stimuli (posibility 1). On the other hand, I could use the individuals responses for the test stimuli but the global mean responses for the reference stimuli (posibility 2). I will calculate attraction index based on both posibilities and look which one works better.

Posibility 1
```{r}
dot_attraction_index_individual <- rep(NaN,length(unique(df_exp$participants)))

for (i in 1:length(unique(df_exp$participants))) {
  
  d_per_participat <- df_exp %>%
    filter(participants== unique(df_exp$participants)[i])
  
  test_stm_dot_p <- d_per_participat %>%
  filter(stimulus == "dot_40_60") %>%
  select(response) 

  reference_few_dot_p <- d_per_participat %>%
    filter(stimulus == "dot_40") %>%
    select(response) 
  
  reference_many_dot_p <- d_per_participat %>%
    filter(stimulus == "dot_60") %>%
    select(response) 
  
dot_attraction_index_individual[i] <- test_stm_dot_p$response/abs(reference_few_dot_p$response - reference_many_dot_p$response)
}

print(dot_attraction_index_individual)

```

I can observe that some results are inf. After look what happened, it seems that some participants gave the same response to the few reference stimuli and to the many reference stimuli. When R divides by 0, it shows inf as the results.

Posibility 2 (less probably that it divides by 0)
```{r}
dot_attraction_index_individual_mean <- rep(NaN,length(unique(df_exp$participants)))
dot_attraction_index_individual_median <- rep(NaN,length(unique(df_exp$participants)))

for (i in 1:length(unique(df_exp$participants))) {
  
  d_per_participat <- df_exp %>%
    filter(participants== unique(df_exp$participants)[i])
  
  test_stm_dot_p <- d_per_participat %>%
  filter(stimulus == "dot_40_60") %>%
  select(response) 
  
  dot_attraction_index_individual_mean[i] <- test_stm_dot_p$response/abs(mean(reference_few_dot$response) - mean(reference_many_dot$response))
  
  dot_attraction_index_individual_median[i] <- test_stm_dot_p$response/abs(median(reference_few_dot$response) - median(reference_many_dot$response))
}

print(dot_attraction_index_individual_mean)
print(dot_attraction_index_individual_median)

```
The second posibility worked better. I will continue with this one.

I will add the individual attraction index as a column
```{r}
df_exp_grouped$dot_attraction_index_individual_mean_d1 <- dot_attraction_index_individual_mean
df_exp_grouped$dot_attraction_index_individual_median_d1 <- dot_attraction_index_individual_median
```

Individual attraction index for faces based on definition 1
```{r}
face_attraction_index_individual_mean <- rep(NaN,length(unique(df_exp$participants)))
face_attraction_index_individual_median <- rep(NaN,length(unique(df_exp$participants)))

for (i in 1:length(unique(df_exp$participants))) {
  
  d_per_participat <- df_exp %>%
    filter(participants== unique(df_exp$participants)[i])
  
  test_stm_face_p <- d_per_participat %>%
  filter(stimulus == "videos/fs1yo.mp4" |stimulus == "videos/fs2yo.mp4") %>%
  select(response) 
  
  face_attraction_index_individual_mean[i] <- test_stm_face_p$response/abs(mean(reference_few_face$response) - mean(reference_many_face$response))
  
  face_attraction_index_individual_median[i] <- test_stm_face_p$response/abs(median(reference_few_face$response) - median(reference_many_face$response))
}

print(face_attraction_index_individual_mean)
print(face_attraction_index_individual_median)

```
I adding the individual attraction index as a column
```{r}
df_exp_grouped$face_attraction_index_individual_mean_d1 <- face_attraction_index_individual_mean
df_exp_grouped$face_attraction_index_individual_median_d1 <- face_attraction_index_individual_median
```


DEFINITION 2 of attraction index

They also defined the attraction index in the following way (it is different with regard to the other definition):

"As a measure of the stability illusion strength, we calculated the bias in age ratings toward the beginning of the movie as an attraction index. We computed the absolute difference between test and reference faces (e.g., old reference age − old test face) and divided that by the total age range (e.g., old reference face − young reference face; white circles in Fig. 1, A and B)." Manassi & Whitney, 2022 

so:

In general for dots
```{r}
## with the mean
print("with the mean: ")
abs(mean(test_stm_dot$response) - mean(reference_many_dot$response))/(mean(reference_many_dot$response) - mean(reference_few_dot$response))
## with the median
print("with the median: ")
abs(median(test_stm_dot$response) - median(reference_many_dot$response))/(median(reference_many_dot$response) - median(reference_few_dot$response))
```
In general for faces
```{r}
## with the mean
print("with the mean: ")
abs(mean(test_stm_face$response) - mean(reference_many_face$response))/(mean(reference_many_face$response) - mean(reference_few_face$response))
## with the median
print("with the median: ")
abs(median(test_stm_face$response) - median(reference_many_face$response))/(median(reference_many_face$response) - median(reference_few_face$response))

```

Per participant with the posibility 2 only - for faces
```{r}
face_attraction_index_individual_mean <- rep(NaN,length(unique(df_exp$participants)))
face_attraction_index_individual_median <- rep(NaN,length(unique(df_exp$participants)))

for (i in 1:length(unique(df_exp$participants))) {
  
  d_per_participat <- df_exp %>%
    filter(participants== unique(df_exp$participants)[i])
  
  test_stm_face_p <- d_per_participat %>%
  filter(stimulus == "videos/fs2yo.mp4" | stimulus == "videos/fs1yo.mp4") %>%
  select(response) 
  
  face_attraction_index_individual_mean[i] <- abs(test_stm_face_p$response - mean(reference_many_face$response))/(mean(reference_many_face$response) - mean(reference_few_face$response))

  
   face_attraction_index_individual_median[i] <- abs(test_stm_face_p$response - median(reference_many_face$response))/(median(reference_many_face$response) - median(reference_few_face$response))
}

print(face_attraction_index_individual_mean)
print(face_attraction_index_individual_median)

```

I will add the individual attraction index based on the definition 2 as a column
```{r}
df_exp_grouped$face_attraction_index_individual_mean_d2 <- face_attraction_index_individual_mean
df_exp_grouped$face_attraction_index_individual_median_d2 <- face_attraction_index_individual_median
```

Per participant with the posibility 2 only - for dots
```{r}
dot_attraction_index_individual_mean <- rep(NaN,length(unique(df_exp$participants)))
dot_attraction_index_individual_median <- rep(NaN,length(unique(df_exp$participants)))

for (i in 1:length(unique(df_exp$participants))) {
  
  d_per_participat <- df_exp %>%
    filter(participants== unique(df_exp$participants)[i])
  
  test_stm_dot_p <- d_per_participat %>%
  filter(stimulus == "dot_40_60") %>%
  select(response) 
  
  dot_attraction_index_individual_mean[i] <- abs(test_stm_dot_p$response - mean(reference_many_dot$response))/(mean(reference_many_dot$response) - mean(reference_few_dot$response))

  
   dot_attraction_index_individual_median[i] <- abs(test_stm_dot_p$response - median(reference_many_dot$response))/(median(reference_many_dot$response) - median(reference_few_dot$response))
}

print(dot_attraction_index_individual_mean)
print(dot_attraction_index_individual_median)

```

I will add the individual attraction index based on the definition 2 as a column
```{r}
df_exp_grouped$dot_attraction_index_individual_mean_d2 <- dot_attraction_index_individual_mean
df_exp_grouped$dot_attraction_index_individual_median_d2 <- dot_attraction_index_individual_median
```


## Exploring the relation between AQ and individual Attraction index


```{r}
d <- data.frame(attractionIndex = c(df_exp_grouped$dot_attraction_index_individual_mean_d1,
                                    df_exp_grouped$dot_attraction_index_individual_median_d1,
                                    df_exp_grouped$dot_attraction_index_individual_mean_d2,
                                    df_exp_grouped$dot_attraction_index_individual_median_d2,
                                    df_exp_grouped$face_attraction_index_individual_mean_d1,
                                    df_exp_grouped$face_attraction_index_individual_median_d1,
                                    df_exp_grouped$face_attraction_index_individual_mean_d2,
                                    df_exp_grouped$face_attraction_index_individual_median_d2
                                    ),
                type_stim = c(rep("Dot", length(unique(df_exp_grouped$participants))*4),
                              rep("Face", length(unique(df_exp_grouped$participants))*4)),
                DefinitionattractionIndex = c(rep("option_1",length(unique(df_exp_grouped$participants))*2),
                                              rep("option_2",length(unique(df_exp_grouped$participants))*2),
                                              rep("option_1",length(unique(df_exp_grouped$participants))*2),
                                              rep("option_2",length(unique(df_exp_grouped$participants))*2)),
                CentralMeasure = c(rep("mean",length(unique(df_exp_grouped$participants))),
                                   rep("median",length(unique(df_exp_grouped$participants))),
                                   rep("mean",length(unique(df_exp_grouped$participants))),
                                   rep("median",length(unique(df_exp_grouped$participants))),
                                   rep("mean",length(unique(df_exp_grouped$participants))),
                                   rep("median",length(unique(df_exp_grouped$participants))),
                                   rep("mean",length(unique(df_exp_grouped$participants))),
                                   rep("median",length(unique(df_exp_grouped$participants)))))
                                           

ggplot(data = d, aes(y = attractionIndex, x = CentralMeasure, fill = DefinitionattractionIndex)) + 
  geom_violin() +
  facet_wrap(~ type_stim) + 
  theme_classic()+
  ggtitle("Individual attraction Index") +
  theme(
    plot.title = element_text(hjust = 0.5)
  )

```
The distribution of individual index attraction seems not normal.



```{r}
# save the df so far
filepath <- root$find_file("pilot/long_df_filtered/df_exp_filter_grouped_long.Rda")
save(df_exp_grouped,file = filepath)
```


## Relationship between AQ and attraction index

# Some visualization 

Faces and AQ

First of all, I will modify the df

```{r}
library(stringr)

# I will work only with faces first
d_faces <- df_exp %>%
  filter(stimulus == "videos/fs1yo.mp4"|
           stimulus == "videos/fs1o.mp4" |
           stimulus == "videos/fs1y.mp4" |
           stimulus == "videos/fs2yo.mp4"|
           stimulus == "videos/fs2o.mp4" |
           stimulus == "videos/fs2y.mp4") %>%
  mutate(face_type = case_when(
  str_detect(stimulus, "(videos/fs1yo.mp4|videos/fs1o.mp4|videos/fs1y.mp4)") ~ 0,
  str_detect(stimulus, "(videos/fs2yo.mp4|videos/fs2o.mp4|videos/fs2y.mp4)") ~ 1,
  TRUE ~ NA 
  ),
  face_age = case_when(
  str_detect(stimulus, "(videos/fs1yo.mp4|videos/fs2yo.mp4)") ~ "morph",
  str_detect(stimulus, "(videos/fs2y.mp4|videos/fs1y.mp4)") ~ "young",
  str_detect(stimulus, "(videos/fs2o.mp4|videos/fs1o.mp4)") ~ "old",
  TRUE ~ NA 
  )) %>%
  select(!(stimulus))

```

Show the data frame new
```{r}
str(d_faces)
head(d_faces)
```

```{r}
d_faces %>% 
  ggplot(aes(x = AQ, y = response, color = face_age)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F) + 
  facet_wrap(~ face_type) + 
  theme_classic()
```


The face 0 and face 1 behave differently regarding AQ (except for the young face).

```{r}
ggplot(data = d_faces, aes(y = response, x = face_age, fill = face_age)) + 
  geom_boxplot() + 
  facet_wrap(~ face_type) + 
  theme_classic()
```
Face 1 does not maximize the effect we are looking for. There does not seem to be much difference between the age reported for young - morph - old. This face was created with a video game program, it doesn't look very real. Think about whether to discard/replace it.

Instead of AQ, we examine the relationship with AQ Attention to Details subscale
```{r}
d_faces %>% 
  ggplot(aes(x = AQ_attencion_detail, y = response, color = face_age)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F) + 
  facet_wrap(~ face_type) + 
  theme_classic()

```


Dots and AQ

```{r}
## crear un data frame para mostrar cuatro lineas, segun media y mediana y segun definicion 1 y 2.
d_dots <- data.frame(AQ = rep(df_exp_grouped$AQ, times= length(unique(df_exp$participants))*4),
                     AQ_attencion_detail = rep(df_exp_grouped$AQ_attencion_detail, times= length(unique(df_exp$participants))*4),
                     AttractionIndex = c(df_exp_grouped$dot_attraction_index_individual_mean_d1,
                                         df_exp_grouped$dot_attraction_index_individual_mean_d2,
                                         df_exp_grouped$dot_attraction_index_individual_median_d1,
                                         df_exp_grouped$dot_attraction_index_individual_median_d2),
                     centralMeasure = c(rep("mean",length(unique(df_exp$participants))*2),
                                        rep("median",length(unique(df_exp$participants))*2)),
                     optionAttractionIndex = c(rep("option_1",length(unique(df_exp$participants))),
                                        rep("option_2",length(unique(df_exp$participants))),
                                        rep("option_1",length(unique(df_exp$participants))),
                                        rep("option_2",length(unique(df_exp$participants))))
                     )

d_dots %>% 
  ggplot(aes(x = AQ, y = AttractionIndex, color = optionAttractionIndex)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F) + 
  facet_wrap(~ centralMeasure)+
  theme_classic()


```

Attraction index options 1 and 2 do not appear to behave equally with respect to AQ.

Exploring attraction index with AQ_attention_detail
```{r}
d_dots %>% 
  ggplot(aes(x = AQ_attencion_detail, y = AttractionIndex, color = optionAttractionIndex)) + 
  geom_point() + 
  geom_smooth(method = "lm", se = F) + 
  facet_wrap(~ centralMeasure)+
  theme_classic()
```



## Now I will try another way to see the bias, after speak with pablo and guille

Exploring the relationship between response based on face_type (face 1 or 2) and face_age (morph, old or young   )
```{r}
ggplot(d_faces, aes(x = face_type, y = response)) +
  geom_point() +  
  geom_smooth(method = "lm") + 
  facet_wrap(~ face_age) +   
  scale_x_continuous(breaks = c(0, 1)) 
```

It doesn't seems to be differences based on the face_type for none of the face_age

Now only the response and face_age
```{r}
library(vioplot)


with(d_faces , vioplot( 
  response[face_age=="morph"] , response[face_age=="old"], response[face_age=="young"],  
  col=rgb(0.1,0.4,0.7,0.7) , names=c("morph","old","young") 
))

```


I will run a graphic asked by yuval
```{r}

d_dots_regression <- df_exp %>%
  filter(stimulus == "dot_40_60" |
           stimulus == "dot_60" |
           stimulus == "dot_40") 

p <- d_dots_regression %>% 
  ggplot(aes(response)) + 
  geom_histogram( fill = "blue", color = "black") +
  ggtitle("Response Histogram") + 
  xlab("Response") + 
  ylab("Count") +
  facet_wrap(~ stimulus) 

# Calcula media y mediana por grupo  
summarized <- d_dots_regression %>% 
  group_by(stimulus) %>% 
  summarize(
    mean = mean(response), 
    median = median(response)
  )

# Agrega las líneas verticales al gráfico base
p + 
  geom_vline(data = summarized, aes(xintercept = mean), color = "black", linetype = "solid") +
  geom_vline(data = summarized, aes(xintercept = median), color = "black", linetype = "dashed") 
```

```{r}

d_faces_plot <- df_exp %>%
  filter(stimulus == "videos/fs1yo.mp4" |
           stimulus == "videos/fs2yo.mp4" |
           stimulus == "videos/fs1y.mp4" |
           stimulus == "videos/fs2y.mp4" |
           stimulus == "videos/fs1o.mp4" |
           stimulus == "videos/fs2o.mp4") 

p <- d_faces_plot %>% 
  ggplot(aes(response)) + 
  geom_histogram( fill = "blue", color = "black") +
  ggtitle("Response Histogram") + 
  xlab("Response") + 
  ylab("Count") +
  facet_wrap(~ stimulus) 

# Calcula media y mediana por grupo  
summarized <- d_faces_plot %>% 
  group_by(stimulus) %>% 
  summarize(
    mean = mean(response), 
    median = median(response)
  )

# Agrega las líneas verticales al gráfico base
p + 
  geom_vline(data = summarized, aes(xintercept = mean), color = "black", linetype = "solid") +
  geom_vline(data = summarized, aes(xintercept = median), color = "black", linetype = "dashed") 
```


Now I will run the frequentist regression model

model 1
```{r}
m_1 <- lm(response ~ face_type + face_age, data= d_faces)
summary(m_1)


```
Ok. When predicting responses, the face_type (1 or 2) is not a significant predictor. Good new

So, can we take it out?

model 2
```{r}
m_2 <- lm(response ~  face_age, data= d_faces)
summary(m_2)
```
Wow, so there is an effect of face_age. Between all categories. More good news.

model 3 (with interactions)
```{r}
d_faces_NotFace1 <- d_faces %>%
  filter(!(face_type == 1))

m_3 <- lm(response ~  face_age* scale(AQ), data= d_faces_NotFace1)
summary(m_3)
```
model 4 
```{r}
m_4 <- lm(response ~  face_type* face_age* scale(AQ), data= d_faces)
summary(m_4)
```

## Now the same for dots

```{r}
d_dots_regression <- df_exp %>%
  filter(stimulus == "dot_40_60" |
           stimulus == "dot_60" |
           stimulus == "dot_40") 

d_dots_regression$AQ <- rep(df_exp_grouped$AQ, each = 3)
d_dots_regression$AQ_attention_detail <- rep(df_exp_grouped$AQ_attencion_detail, each = 3)


# Reorder the categorical variable
d_dots_regression$stimulus <- as.factor(d_dots_regression$stimulus)
d_dots_regression <- d_dots_regression %>%
  mutate(stimulus = relevel(stimulus, ref = "dot_40_60"))
```

model 1
```{r}
m_1_dots <- lm(response ~  stimulus, data= d_dots_regression)
summary(m_1_dots)
```


model 2 - m_1_dots but with AQ
```{r}
m_2_dots <- lm(response ~  stimulus*AQ, data= d_dots_regression)
summary(m_2_dots)
```

model 3 - m_1_dots but with AQ
```{r}
m_3_dots <- lm(response ~  stimulus*AQ_attention_detail, data= d_dots_regression)
summary(m_3_dots)
```

## Now bayes way

Libraries
```{r}
library(bayesrules)
library(tidyverse)
library(rstan)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(janitor)
library(broom.mixed)
```

Lets continue with model 2

The prior for the intercept will be based on the original paper of manassi and whitney 2022.
The young face of face 1 was rating as 13 years old
The old face of face 1 was rating as 25.5 years old
The morph face of face 1 was rating as 20.2 years old

The young face of face 2 (high noise) was rating as 14.8 years old
The old face of face 2 (high noise) was rating as 23.8 years old
The morph face of face 2 was rating as 20.3 years old

We have no report of the standar deviation of these means, I will use weakly informative prior.

In the model 2 (response ~  face_age), the intercept is the mean of the response when x is 0 (the morph stimuli is the baseline here). So, combining both mean of the morph stimulus (face 1 and 2) we have a mean of 20.25 for the morph stimuli 

I will see if the prior is ok with a sd of 10 for the intercept
```{r}
plot_normal(20.25,10)
```
We have negative results as possible but they are unlikely.

We realized that can take out the young face in this way of observe the bias. It is useful when we want to calculate the attraction index as defined by manassi and whytney 2022, but not now
```{r}
d_faces_NotYoung <- d_faces %>%
  filter(!(face_age == "young"))
```



```{r}

m_2_bayesian <- stan_glm(
  log(response) ~  face_age, 
  data= d_faces_NotYoung, family = gaussian,
  prior_intercept = normal(20.25,10),
  prior = normal(0,2),
  prior_aux = exponential(1, autoscale = TRUE),
  chains = 4, iter = 5000*2, seed = 1948,
  prior_PD = FALSE
)

## me tira error, http://mc-stan.org/rstanarm/reference/priors.html muestra que no existe
## la posibilidad de elegir priors lognormal o halfnomal
```

prior check
```{r}
# Prior specification
prior_summary(m_2_bayesian)
```

MCMC diagnostics

```{r}
mcmc_trace(m_2_bayesian, size = 0.1)
mcmc_dens_overlay(m_2_bayesian)
mcmc_acf(m_2_bayesian)
neff_ratio(m_2_bayesian)
rhat(m_2_bayesian)
```


Exploring postriors
```{r}
head(as.data.frame(m_2_bayesian),10)
```

Posterior summary statistics
```{r}
tidy(m_2_bayesian, effects = c("fixed", "aux"),
     conf.int = TRUE, conf.level = 0.80)
```


```{r}
pp_check(m_2_bayesian)
```


```{r}
mcmc_areas(m_2_bayesian) +
  ggplot2::scale_y_discrete(labels = c("morph", "old", "sigma")) + 
  xlab("response")
```

